%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://}{\Large}} & Email : \href{mailto:}{email@email.com}\\
%   \href{http://web.com/}{http://www.web.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Jayant Dahiya} \\ \vspace{1pt}
    \small \href{tel://+91-7015609505}{\underline{+91-70156 09505}} 
    $|$ 
    \href{jayantdahiyadev@gmail.com}{\underline{jayantdahiyadev@gmail.com}} 
    $|$ 
    \href{https://linkedin.com/in/dahiyajayant}{\underline{linkedin.com/in/JayantDahiya}} 
    $|$
    \href{https://github.com/jayantdahiya}{\underline{github.com/JayantDahiya}}
\end{center}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, TypeScript, Solidity, Python, HTML/CSS, SQL} \\
     \textbf{Frameworks}{: React, Node.js, FastAPI, TailwindCSS, GraphQL, Socket.io, Three.js} \\
     \textbf{Developer Tools}{: Docker, Google Cloud Platform, AWS, Firebase, Cloudflare Services, Git} \\
     \textbf{Libraries}{: Redux, Pandas, NumPy, Seaborn}
    }}
 \end{itemize}



%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
      {Frontend Developer}{May 2022 -- Sept 2023}
      {Freelance}{Remote}
      \resumeItemListStart
        \resumeItem{Contributed and managed client on a portfolio management startup's MVP build on MERN stack, leading to a 15 percent equity offer from investors.}
        \resumeItem{Worked on a branding project for a France-based production agency, creating brand identity and a landing page that boosted client and audience generation.}
        \resumeItem{Assisted in the development of a smart contract for a real estate registry startup in Brazil, ensuring secure property registrations with Solidity, Hardhat and Alchemy.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Associate}{Sept 2021 -- May 2022}
      {OLA Cabs}{Remote}
      \resumeItemListStart
        \resumeItem{Resolved production level issues in applications using REST API(as JSON) with: Graylog and Postman}
        \resumeItem{Improved application stability via Python data analysis (Pandas, Seaborn, Matplotlib), reducing production issues by 20 Percent.}
        \resumeItem{Ensured performance of the Services and Database with tools: Grafana, New Relic and Apache Hive.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
% -------------------------------------------


    \resumeSubheading
      {Software Developer}{Jan 2021 -- Aug 2021}
      {SitDown Design LLC}{New Delhi}
      \resumeItemListStart
        \resumeItem{Collaborated with cross-functional teams to enhance brand UI/UX, translating client needs into actionable design and development tasks.}
        \resumeItem{Utilized Firebase Analytics to analyze user behaviour, driving data-driven design decisions for improved user engagement.}
        \resumeItem{Gained exposure to Agile/SCRUM practices and contributed to effective project management, ensuring timely delivery of projects.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Developer (Founding Team)}{Oct 2020 -- Aug 2021}
      {ATTREQ Pvt. Ltd.}{New Delhi}
      \resumeItemListStart
        \resumeItem{Led the development of MVP frontend and APIs using React with PWA integration.}
        \resumeItem{Collaborated on improving backend object detection models based on RCNN, utilizing AWS p2 instances.}
        \resumeItem{Enhanced object detection models with K-Means algorithm and collaborative filtering techniques.}
      \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AnonNews} $|$ \emph{React, TailwindCSS, Solidity, IPFS}}{\href{https://github.com/jayantdahiya/AnonNews}{\underline{GitHub}} $ | $ \href{https://anon-news.web.app/}{\underline{Website}}}
          \resumeItemListStart
            \resumeItem{Developed an anonymous news sharing platform utilizing blockchain technology, allowing users to post news anonymously via crypto wallets with associated gas fees.}
            \resumeItem{Created the project's frontend using React, TailwindCSS, and ethers.js, while the backend consisted of a Solidity smart contract hosted on Polygon Mumbai test chain through Alchemy.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Market-Maven} $|$ \emph{React, TailwindCSS, Python, FastAPI, Firebase, Nginx, Docker}}{\href{https://github.com/jayantdahiya/Market-Maven}{\underline{GitHub}} $ | $ \href{https://marketmavenai.web.app}{\underline{Website}}}
          \resumeItemListStart
            \resumeItem{Developed a stock forecasting web app employing time-series prediction models such as Facebook's Prophet, accurately predicting trends for user-input ticker.}
            \resumeItem{Implemented on-premise backend server serving REST API(as JSON) using FastAPI with an NGINX proxy, the API is served securely through Cloudflare Tunnels in SSL-encrypted format to the mainnet. }
          \resumeItemListEnd
\resumeSubHeadingListEnd



%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Lovely Professional University}{Punjab}
      {Bachelor of Technology in Computer Science and Engineering}{Aug. 2017 -- Aug 2021}
  \resumeSubHeadingListEnd
%

%-------------------------------------------
\end{document}